\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-28 doc/sui14/iteration1.tex
fix } mismatch
use 0.95 for all figures
fixed } again

\subsection{Technique}
In our first implementation, we use IR for scanning as described in the previous section. For the refinement stage, we simply show a list of the subset of targets that have received IR signals on the Glass display. Users swipe to select from that list and tap to confirm the intended target.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/study-layout1.png}
\caption{In the targeting study, participants were asked to find and select one of 10 targets in the lab environment.}
\label{fig:targeting-study-layout}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selection} is shown on the left. The center is the median value, and the mean value is shown using white dashed lines. The cumulative distributions are on the right.}
\label{fig:ir_vs_list}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1b.pdf}
\caption{Boxplot and CDF of target acquisition time when refinement is needed or not in {\em IR selection}}.
\label{fig:with_without_refinement}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/result_study1c.pdf}
\caption{Times taken to select a device vs.~its order in the {\em list selection}. The dotted line is a linear fit between the average time and target orders in the list. Two horizontal solid lines are the average target acquisition times in {\em Naive IR} when refinement is needed or not.}
\label{fig:time-vs-list-order}
\end{figure}

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, \changes{IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition.}

>>>>

\vfill
\subsection{Technique}
In our first implementation, we use IR for scanning as described in the previous section. For the refinement stage, we simply show a list of the subset of targets that have received IR signals on the Glass display. Users swipe to select from that list and tap to confirm the intended target.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/study-layout1.png}
\caption{In the targeting study, participants were asked to find and select one of 10 targets in the lab environment.}
\label{fig:targeting-study-layout}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/result_study1a.pdf}
\caption{Boxplot of target acquisition time for {\em IR selection} and {\em list selection} is shown on the left. The center is the median value, and the mean value is shown using white dashed lines. The cumulative distributions are on the right.}
\label{fig:ir_vs_list}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/result_study1b.pdf}
\caption{Boxplot and CDF of target acquisition time when refinement is needed or not in {\em IR selection}}.
\label{fig:with_without_refinement}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/result_study1c.pdf}
\caption{Times taken to select a device vs.~its order in the {\em list selection}. The dotted line is a linear fit between the average time and target orders in the list. Two horizontal solid lines are the average target acquisition times in {\em Naive IR} when refinement is needed or not.}
\label{fig:time-vs-list-order}
\end{figure}

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, \changes{IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}}.
